Issues with Dynamical Measurements Across the Disk

### 2019-03-18 paper/ms.tex
Change ref to m12i/f/m

\begin{deluxetable*}{cccccc}
\tablecaption{Stellar disk scale heights of the real Milky Way and the
simulated galaxies considered in this work.\label{tab:scale_height}}
\tablehead{\colhead{galaxy} & \colhead{cold\tablenotemark{a} gas disk} & \colhead{stellar thin disk} & \colhead{stellar thick disk} & \colhead{cold gas softening length} & \colhead{stellar softening length} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{b} & 40 & 300 & 900 & 0 & 0 \\
\mi\tablenotemark{c} & 800\tablenotemark{d} & 480 & 2000 & 12.4 & 11.2 \\
\mf\tablenotemark{c} & 360 & 440 & 1280 & 12.5 & 11.2 \\
\mm\tablenotemark{c} & 250 & 290 & 1030 &10.3 & 11.2 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}
\tablenotetext{a}{$T<1000$ K}
\tablenotetext{b}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{c}{\citet{2018arXiv180610564S}}
\tablenotetext{d}{The azimuthally averaged gas vertical density profile in
m12i is nearly constant to this height, though individual regions show smaller
scale heights and dense clouds.}
\end{deluxetable*}

@@

The situation is more forgiving for the study of thick-disk-like orbits, where
an $\mathcal{O}(1)$ systematic error in $J_z$ requires a larger midplane
deviation (\thickcolor{} horizontal line in Figure~\ref{fig:range_deltaphi}).
In fact, the range of midplane variation in m12i just barely saturates to
cause such an error in $J_z$, with the midplane variation in m12f and m12m
never reaching such a value. For stars on halo-like orbits, extending the
local coordinate system globally is not likely to cause serious problems,
since the midplane deviations are relatively small compared to those needed to
produce $\mathcal{O}(1)$ systematic errors in the actions (\halocolor{}
horizontal line in Figure \ref{fig:range_deltaphi}). However, we caution that
the tendency of these midplane deviations is to \emph{inflate} the value of
$J_z$ whenever the midplane deviation is $\gtrsim z_{\text{max}}$, scattering
them into the region of action space normally associated with different
stellar populations and possibly contributing to confusion there. This
inflation is extremely non-Gaussian (as the induced error is for all orbits,
e.g. Figure~\ref{fig:Jz_hist}), and is particularly troubling for the case of
thin disk stars, where the necessary midplane deviation is
$\sim50\textup{--}100\,\pc$.

>>>>

\begin{deluxetable*}{cccccc}
\tablecaption{Stellar disk scale heights of the real Milky Way and the
simulated galaxies considered in this work.\label{tab:scale_height}}
\tablehead{\colhead{galaxy} & \colhead{cold\tablenotemark{a} gas disk} & \colhead{stellar thin disk} & \colhead{stellar thick disk} & \colhead{cold gas softening length} & \colhead{stellar softening length} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{b} & 40 & 300 & 900 & 0 & 0 \\
\mi\tablenotemark{c} & 800\tablenotemark{d} & 480 & 2000 & 12.4 & 11.2 \\
\mf\tablenotemark{c} & 360 & 440 & 1280 & 12.5 & 11.2 \\
\mm\tablenotemark{c} & 250 & 290 & 1030 &10.3 & 11.2 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}
\tablenotetext{a}{$T<1000$ K}
\tablenotetext{b}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{c}{\citet{2018arXiv180610564S}}
\tablenotetext{d}{The azimuthally averaged gas vertical density profile in
\mi{} is nearly constant to this height, though individual regions show smaller
scale heights and dense clouds.}
\end{deluxetable*}

@@

The situation is more forgiving for the study of thick-disk-like orbits, where
an $\mathcal{O}(1)$ systematic error in $J_z$ requires a larger midplane
deviation (\thickcolor{} horizontal line in Figure~\ref{fig:range_deltaphi}).
In fact, the range of midplane variation in \mi{} just barely saturates to
cause such an error in $J_z$, with the midplane variation in \mf{} and \mm{}
never reaching such a value. For stars on halo-like orbits, extending the
local coordinate system globally is not likely to cause serious problems,
since the midplane deviations are relatively small compared to those needed to
produce $\mathcal{O}(1)$ systematic errors in the actions (\halocolor{}
horizontal line in Figure \ref{fig:range_deltaphi}). However, we caution that
the tendency of these midplane deviations is to \emph{inflate} the value of
$J_z$ whenever the midplane deviation is $\gtrsim z_{\text{max}}$, scattering
them into the region of action space normally associated with different
stellar populations and possibly contributing to confusion there. This
inflation is extremely non-Gaussian (as the induced error is for all orbits,
e.g. Figure~\ref{fig:Jz_hist}), and is particularly troubling for the case of
thin disk stars, where the necessary midplane deviation is
$\sim50\textup{--}100\,\pc$.
